Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-20 manuscript/paper-tycho.tex
Telecon notes; Bmin=0, l_ad/l_diff/etc plots
Add notes/todos from telecon; add cells/scripts addressing todos
Fit data with Bmin=0, compute/compare relevant lengthscales
Fix paper text; cut many tables/plots, update plots to eta2=1
Re-add srcutlog table to paper

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citep{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) allows fine sampling of the remnant rims.  Furthermore, Tycho
is a prime target of study to determine whether hadrons are being accelerated
in historic SNRs \citep[and references therein]{morlino2012}; understanding the
acceleration process for electrons will also bear upon our understanding of CR
acceleration in Tycho.

@@

We model electron advection and diffusion downstream of the shock (i.e., for
$x>0$ only) with a 1-D steady-state plane transport equation:
\begin{equation} \label{eq:model}
    v_d \frac{\ptl f}{\ptl x}
    - \frac{\ptl}{\ptl x} \left(D\frac{\ptl f}{\ptl x}\right)
    - \frac{\ptl}{\ptl E} \left(bB^2E^2f\right)
    = K_0 E^{-s} e^{-E/\Ecut} \delta(x) ;
\end{equation}
this follows the work of \citet{webb1984, berezhko2004, cassam-chenai2007,
morlino2010, rettig2012}.  Here $f = f(E,x)$ is electron distribution as a
function of electron energy $E$ and downstream distance $x$, $D$ is the
diffusion coefficient, and $v_d$ is plasma velocity downstream of the shock.
The constant $b = 1.57 \times 10^{-3}$ in CGS units arises from synchrotron
power loss at electron energy $E$ (i.e., $\ptl E/\ptl t = b B^2 E^2$).
We have assumed isotropic diffusion and consider only processes operating
downstream of the shock.  More sophisticated treatments may explicitly treat
magnetic fields and diffusion across the shock, plasma streaming instabilities
and particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

To determine rim profiles and widths, we numerically solve for electron
distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
and \citet{rettig2012}; the solutions are given by \citetalias{ressler2014}
using notation similar to ours.  We note, however, that the solutions for
$f(E,x)$ in equation~\eqref{eq:model} are derived assuming that $D(x) B^2(x)$
is constant \citep{lerche1980}.  The electron distribution may be integrated
over the one-particle synchrotron emissivity $G(y)$ to obtain the ``total''
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ with $K_{5/3}(z)$ a modified Bessel
function of the second kind \citep{pacholczyk1970}.  Integrating emissivity
over lines of sight for a spherical remnant yields intensity as a function of
radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                   j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  Finally, we compute the full width
at half maximum (FWHM) of the resulting intensity profile to compare to our
measurements of rim width.

@@

% e- cut-off energy result
With a diffusion coefficient in hand, we may determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated to higher energies and the energy spectrum drops off steeply.  The
cut-off energy is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
shock with compression ratio 4 and isotropic magnetic turbulence on both sides
of the shock.

@@

% Intuition: transport lengthscales in the absence of damping
To better intuit the effects of advection and diffusion on rim widths, we
consider advective and diffusive lengthscales for electron transport given as:
\begin{equation} \label{eq:lad}
    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
\end{equation}
and
\begin{equation} \label{eq:ldiff}
    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
\end{equation}
The characteristic time is the synchrotron cooling time
$\tsynch = 1 / (b B^2 E)$ with $b = 1.57 \times 10^{-3}$.
If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$.  Diffusion
increases $\mE$ monotonically from $-1/2$ to a value between $-1/4$ and $1/4$
for $\mu = 0$ and $2$ respectively \citepalias[Figure 3]{ressler2014}.  The
presence of an electron energy cut-off, decreases $\mE$ slightly in all cases
due to the decreased number of electrons and hence thinner rims at higher
energies \citepalias[Figure 5]{ressler2014}.

@@

We measured synchrotron rim full widths at half maximum (FWHMs) from an
archival \Chandra ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: J. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excluded the 1.7--2 keV energy range to avoid \ion{Si}{13} (He$\alpha$)
emission at 1.85 keV, prevalent in the remnant's thermal ejecta, which
might contaminate our nonthermal profile measurements.

@@

\begin{figure*}%[ht]
    \iftoggle{manuscript}{
        \epsscale{1}
    }{}
    \plotone{figures/prfs_01.pdf}
    \plotone{figures/prfs_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
        from left to right.  Data points in red were excluded from profile
        fitting domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We fixed $a_b$ at $14$ different values between $0.5$ and $0.002$ (sampling
most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
free.  Formally, we do not seek a best fit value of damping length $a_b$, so
our ``best'' damping fits report the value of $a_b$ yielding the smallest
$\chi^2$ value.  Finally, $\mu = 1$ was fixed for all damped fits.

We required $\eta_2$ to be positive in all fits.  We also deemed
best-fit and error bound values with $\eta_2 \geq 10^5$ and $B_0 \geq 10
\unit{mG}$ to be effectively unconstrained. % Change this if needed.

@@

% Explain our approach
We tabulate and plot detailed results for Regions 1 and 16, the same regions
shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
subset of our regions, qualitative trends in fit parameters were comparable in
most regions; our most salient observations, discussed below, are well
exemplified by Regions 1 and 16.  Best fit results for all regions are
summarized in Figure~\ref{fig:fits-all} and Tables~\ref{tab:fits-all},
\ref{tab:fits-all-eta2one}.  In all tables, we report values of $\chi^2$ rather
than $\chi^2_\mt{red}$ to ease comparison of different fits, as we often
manually stepped one or two parameters that were held constant in fitting.

% Best fit model results and tables for Regions 1, 16.
% Explain a bit about model shapes, and the relative similarity in shapes
Modeled profiles with best fit FWHMs for Regions 1 and 16 are plotted in
Figure~\ref{fig:rims}, and their derived best-fit FWHM-energy curves
are plotted in Figure~\ref{fig:fits} alongside measured FWHMs.
The best fit model profiles do not quite match measured rim profiles
(Figure~\ref{fig:profiles}).  Our transport equation does not account for
diffusive transport upstream of the shock, projection effects from shock
ripples or other structure, and thermal emission downstream of the thin rim.
Fitting to multiple FWHM measurements should be robust to these effects as
compared to directly fitting entire rim profiles to model predictions.
Although Figure~\ref{fig:rims} plots model profiles for $\mu = 1$ only, the
best-fit FWHM-energy curves show that model profiles for $\mu \neq 1$ give very
similar FWHM-energy dependence.

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.7}
        \plotone{figures/prfs-fit-01.pdf} \\
        \plotone{figures/prfs-fit-16.pdf}
        \epsscale{1}
    }{
        \plotone{figures/prfs-fit-01.pdf} \\
        \plotone{figures/prfs-fit-16.pdf}
    }
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
        damped profiles indicate the magnetic field damping lengthscale $a_b$.
        \label{fig:rims}}
\end{figure}

\begin{figure}
    \centering
    %\epsscale{0.45}  % For manuscript layout only!
    \iftoggle{manuscript}{
        \includegraphics[width=0.46\textwidth]{figures/energywidth-01.pdf}
        \includegraphics[width=0.46\textwidth]{figures/energywidth-16.pdf}
    }{
        \includegraphics[width=0.23\textwidth]{figures/energywidth-01.pdf}
        \includegraphics[width=0.23\textwidth]{figures/energywidth-16.pdf}
    }
    \caption{Loss-limited rim width predictions as a function of energy for
    Regions 1 (top) and 16 (bottom), with measured data.  Dotted/dashed curves
    plot pure loss-limited fits with varying $\mu$, solid curve plots estimated
    best moderately damped fit ($a_b < 0.01$) with $\mu = 1$.  Relevant fit
    parameters are given in Tables~\ref{tab:fits-loss} and \ref{tab:fits-damp}.
    Note that ordinate FWHM axes are not the same and are offset from the
    origin to better show model predictions and data variation.
    \label{fig:fits}}
\end{figure}

\begin{figure*}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.8\textwidth]{figures/energywidth-subplot.pdf}
    }{
        \plotone{figures/energywidth-subplot.pdf}
    }
    \caption{Rim width predictions for loss-limited and damped fits with
    $\mu = 1$ fixed for all regions.  Neither loss-limited nor damped fits
    are clearly favored in describing the data.  Some damped model predictions
    (e.g., Region 5) are not given at low energies if FWHMs cannot be
    calculated for model profiles (modeled intensity behind thin rim exceeds
    half-maximum of rim peak within model domain of $\abt 20\arcsec$).
    Corresponding best fit parameters are given in Table~\ref{tab:fits-all}.
    As in Figure~\ref{fig:fits}, $y$-axis limits vary and are offset from the
    origin to better show model predictions and data.
    \label{fig:fits-all}}
\end{figure*}

@@

% Fit results for ALL regions, mu = 1, loss-limited and damped
% NOTE keep # of dofs updated
\begin{table}
    \iftoggle{manuscript}{
        \scriptsize
    }{
        \tiny
    }
    \centering
    \caption{Best model fits for all regions, $\mu = 1$
    \label{tab:fits-all}}
    \input{tab-fits-all.tex}
    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
    best damped fits select best $a_b$ value below $0.01$ from the range shown
    in Table~\ref{tab:fits-damp}, enforcing moderate damping.  Fits for Regions
    1, 2, 12, 18 have 2 dofs; all others have 3.  The manual selection of a
    best $a_b$ value may be construed as removing one more dof.}
    % NOTE UPDATE AS FWHMS UPDATED
\end{table}

In Table~\ref{tab:fits-all-eta2one} we also present best loss-limited and
damped fits with $\eta_2 = 1$ fixed.  As before, both loss-limited and damped
models are equally capable of fitting the observed data.

% As above but with eta2=1 fixed!
\begin{table}
    \scriptsize
    \centering
    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$
    \label{tab:fits-all-eta2one}}
    \input{tab-fits-all-eta2one.tex}
    \tablecomments{See comments on Table~\ref{tab:fits-all}.  Fits have
    one additional dof as $\eta_2 = 1$ is fixed.}
\end{table}

@@

% First address the broad trend of leveling energy dependence in mE)
We suggest that the observed decrease in $|\mE|$ with increasing energy
(Table~\ref{tab:fwhms}) is caused by diffusion, which weakens width-energy
dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy.
% TODO citation if you can find it...
Diffusion should begin overtaking advection and push $\mE$ towards $0$ in soft
X-rays, as opposed to $\mE \abt -0.5$ expected for strong advection
(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
consistent with the framework of diffusive shock acceleration.

@@

% Then, degeneracy modification in the damping model
The degeneracy in $B_0$ and $\eta_2$ is modified by the presence of damping.
For small values of $a_b$ (strong damping), increased diffusion $\eta_2$ can
cause rim widths to narrow counterintuitively.  Speculatively, spatial
variation of the diffusion coefficient, which gives rise to a
term $(\ptl D(x) / \ptl x) (\ptl f/\ptl x)$ in equation~\eqref{eq:model}, may
oppose downstream advection by decreasing an effective velocity $v_d - \ptl
D(x) / \ptl x$ and thus require thinner rims as $\eta_2$ and $\ptl D(x) / \ptl
x$ increase.

@@

% -------------------------------
% srcutlog and spectral variation
% -------------------------------
\subsection{Spectral constraints on model fits}

\subsubsection{Synchrotron cut-off measurements}

@@

The radio and X-ray profile modeling here contrasts strongly with our previous
width-energy fitting from X-ray measurements alone, which neglected profile
shape in favor of more robust FWHM measurements.  Manually fitting profiles
allows us to consider radio and X-ray filaments that do not have well-defined
FWHMs, especially as radio rims do not fall below 50\% of the peak emission.
We can also use profiles from regions not previously considered due to the lack
of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.

>>>>

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citep{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
allows fine sampling of the remnant rims.  Furthermore, Tycho
is a prime target of study to determine whether hadrons are being accelerated
in historic SNRs \citep[and references therein]{morlino2012}; understanding the
acceleration process for electrons will also bear upon our understanding of CR
acceleration in Tycho.

@@

We model electron advection and diffusion downstream of the shock (i.e., for
$x>0$ only) with a 1-D steady-state plane transport equation:
\begin{equation} \label{eq:model}
    v_d \frac{\ptl f}{\ptl x}
    - \frac{\ptl}{\ptl x} \left(D\frac{\ptl f}{\ptl x}\right)
    - \frac{\ptl}{\ptl E} \left(bB^2E^2f\right)
    = K_0 E^{-s} e^{-E/\Ecut} \delta(x) ;
\end{equation}
this follows the work of \citet{webb1984, berezhko2004, cassam-chenai2007,
morlino2010, rettig2012}.  Here $f = f(E,x)$ is electron distribution as a
function of electron energy $E$ and downstream distance $x$, $D$ is the
diffusion coefficient, and $v_d$ is plasma velocity downstream of the shock.
The constant $b = 1.57 \times 10^{-3}$ in CGS units arises from synchrotron
power loss at electron energy $E$ (i.e., $\ptl E/\ptl t = b B^2 E^2$).
We have assumed isotropic diffusion and consider only processes operating
downstream of the shock.  We also do not incorporate models for self-similar
velocity and magnetic field evolution downstream of a spherical shock (e.g.,
the well-known Sedov-Taylor solution).  A plane flow approximation should be
reasonable as we only consider synchrotron emission within 10\% of the shock
radius, $r_s$, from the forward shock.  % TODO CITATION AND REWORD.
More sophisticated treatments may explicitly treat
magnetic fields and diffusion across the shock, plasma streaming instabilities
and particle losses, anisotropic diffusion, injection/acceleration efficiency,
and other details in great depth \citep[e.g.,][and references
therein]{reville2013, bykov2014, ferrand2014}.

To determine rim profiles and widths, we numerically solve for electron
distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
and \citet{rettig2012}; the solutions are given by \citetalias{ressler2014}
using notation similar to ours.  We note, however, that the solutions for
$f(E,x)$ in equation~\eqref{eq:model} are derived assuming that $D(x) B^2(x)$
is constant \citep{lerche1980}.  The electron distribution may be integrated
over the one-particle synchrotron emissivity $G(y)$ to obtain the ``total''
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ with $K_{5/3}(z)$ a modified Bessel
function of the second kind \citep{pacholczyk1970}.  Integrating emissivity
over lines of sight for a spherical remnant yields intensity as a function of
radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                   j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate and $r_s$ is shock radius.  Finally,
we compute the full width at half maximum (FWHM) of the resulting intensity
profile to compare to our measurements of rim width.

@@

% e- cut-off energy result
With a diffusion coefficient in hand, we may determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated to higher energies and the energy spectrum drops off steeply.  The
cut-off energy is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
Here $B_0$ is the magnetic field immediately downstream of the shock, i.e.
$B_0 = B(x=0)$.
This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
shock with compression ratio 4 and isotropic magnetic turbulence on both sides
of the shock.

@@

% Intuition: transport lengthscales in the absence of damping
To better intuit the effects of advection and diffusion on rim widths, we
consider advective and diffusive lengthscales for electron transport given as:
\begin{equation} \label{eq:lad}
    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
% = \frac{v_d \sqrt{c_m}}{b} B_0^{-3/2} \nu^{-1/2}
\end{equation}
and
\begin{equation} \label{eq:ldiff}
    l_{\mt{diff}} = \sqrt{D \tsynch}
                  \propto \eta^{1/2} B_0^{-(\mu+5)/4} \nu^{(\mu-1)/4}
% = (C_d/b)^{1/2} c_m^{-(\mu-1)/4} \eta^{1/2} B_0^{-(\mu+5)/4} \nu^{(\mu-1)/4}
\end{equation}
The characteristic time is the synchrotron cooling time
$\tsynch = 1 / (b B^2 E)$ with $b = 1.57 \times 10^{-3}$.
For $\mu = 1$, note that $l_{\mt{diff}}$ is independent of $\nu$ and
$l_{\mt{diff}} \propto B_0^{-3/2}$ matches the scaling of $l_{\mt{ad}}$.
If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$.  Diffusion
increases $\mE$ monotonically from $-1/2$ to a value between $-1/4$ and $1/4$
for $\mu = 0$ and $2$ respectively \citepalias[Figure 3]{ressler2014}.  The
presence of an electron energy cut-off, decreases $\mE$ slightly in all cases
due to the decreased number of electrons and hence thinner rims at higher
energies \citepalias[Figure 5]{ressler2014}.

@@

We measured synchrotron rim full widths at half maximum (FWHMs) from an
archival \Chandra ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: J. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}); \citet{eriksen2011}
present additional observation information.
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excluded the 1.7--2 keV energy range to avoid \ion{Si}{13} (He$\alpha$)
emission at 1.85 keV, prevalent in the remnant's thermal ejecta, which
might contaminate our nonthermal profile measurements.

@@

\begin{figure*}%[ht]
    \iftoggle{manuscript}{
        \epsscale{1}
    }{}
    \plotone{figures/prfs_01.pdf}
    \plotone{figures/prfs_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 16 (bottom).  Hereafter, we use
        Regions 1 and 16 to illustrate results for profiles of differing
        quality and absolute width.  We could not measure a $0.7$--$1
        \unit{keV}$ FWHM in Region 1, reflected in Table~\ref{tab:fwhms}.  Data
        in red were excluded from profile fit domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We stepped $a_b$ through $14$ different values between $0.5$ and $0.002$ (sampling
most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
free.  For best fits, we report the value of $a_b$ yielding the smallest
$\chi^2$ value, noting that our $a_b$ sampling is coarse.

We required $\eta_2$ to be positive in all fits.  We also deemed
best-fit and error bound values with $\eta_2 \geq 10^5$ and $B_0 \geq 10
\unit{mG}$ to be effectively unconstrained. % Change this if needed.
% TODO "best-fit" vs. "best fit"... argh

@@

% TODO we must restructure this text, since we are now not emphasizing Regions
% 1/16 alone quite as much.  Just synthesize all together, use fig:fits to
% explain that mu dependence is very weak.

% TODO we could rewrite this all to say up front -- we work with eta2=1 unless
% otherwise stated.  But that should wait until I review the new chain of
% tables / figures w/ Rob and Brian.

% Explain our approach
We tabulate and plot detailed results for Regions 1 and 16, the same regions
shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
subset of our regions, qualitative trends in fit parameters were comparable in
most regions; our most salient observations, discussed below, are well
exemplified by Regions 1 and 16.  Best fit results for all regions are
summarized in Figure~\ref{fig:fits-all} and Table~\ref{tab:fits-all-eta2one}.
In all tables, we report values of $\chi^2$ rather
than $\chi^2_\mt{red}$ to ease comparison of different fits, as we often
manually stepped one or two parameters that were held constant in fitting.

% Best fit model results and tables for Regions 1, 16.
% Explain a bit about model shapes, and the relative similarity in shapes
The best-fit FWHM-energy curves for Regions 1 and 16 are plotted in
Figure~\ref{fig:fits} alongside measured FWHMs.
Our transport equation does not account for
diffusive transport upstream of the shock, projection effects from shock
ripples or other structure, and thermal emission downstream of the thin rim.
Fitting to multiple FWHM measurements should be robust to these effects as
compared to directly fitting entire rim profiles to model predictions.

\begin{figure}
    \centering
    %\epsscale{0.45}  % For manuscript layout only!
    \iftoggle{manuscript}{
        \includegraphics[width=0.46\textwidth]{figures/energywidth-eta2one-01.pdf}
        \includegraphics[width=0.46\textwidth]{figures/energywidth-eta2one-16.pdf}
    }{
        \includegraphics[width=0.23\textwidth]{figures/energywidth-eta2one-01.pdf}
        \includegraphics[width=0.23\textwidth]{figures/energywidth-eta2one-16.pdf}
    }
    \caption{Best fit rim width-energy predictions for
    Regions 1 (top) and 16 (bottom), with measured data.  Dotted/dashed curves
    plot pure loss-limited fits with varying $\mu$, solid curve plots estimated
    best moderately damped fit ($a_b < 0.01$) with $\mu = 1$.  All fits hold
    $\eta_2 = 1$ fixed; model parameters are given in
    Tables~\ref{tab:fits-all-eta2one}.
    Note that ordinate FWHM axes are not the same and are offset from the
    origin to better show model predictions and data variation.
    \label{fig:fits}}
\end{figure}

\begin{figure*}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.8\textwidth]{figures/energywidth-subplot.pdf}
    }{
        \plotone{figures/energywidth-subplot.pdf}
    }
    \caption{Rim width predictions for loss-limited and damped fits with
    $\mu = 1$ and $\eta_2=1$ fixed for all regions.  Neither loss-limited nor
    damped fits
    are clearly favored in describing the data.  Some damped model predictions
    (e.g., Region 5) are not given at low energies if FWHMs cannot be
    calculated for model profiles (modeled intensity behind thin rim exceeds
    half-maximum of rim peak within model domain of $\abt 20\arcsec$).
    Corresponding best fit parameters are given in
    Table~\ref{tab:fits-all-eta2one}.
    As in Figure~\ref{fig:fits}, $y$-axis limits vary and are offset from the
    origin to better show model predictions and data.
    \label{fig:fits-all}}
\end{figure*}

@@

% Fit results for ALL regions, mu = 1, eta2 free, loss-limited and damped
% NOTE keep # of dofs updated
%\begin{table}
%    \iftoggle{manuscript}{
%        \scriptsize
%    }{
%        \tiny
%    }
%    \centering
%    \caption{Best model fits for all regions, $\mu = 1$
%    \label{tab:fits-all}}
%    \input{tab-fits-all.tex}
%    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
%    best damped fits select best $a_b$ value below $0.01$ from the range shown
%    in Table~\ref{tab:fits-damp}, enforcing moderate damping.  Fits for Regions
%    1, 2, 12, 18 have 2 dofs; all others have 3.  The manual selection of a
%    best $a_b$ value may be construed as removing one more dof.}
%    % NOTE UPDATE AS FWHMS UPDATED
%\end{table}

In Table~\ref{tab:fits-all-eta2one} we present best loss-limited and
damped fits with $\eta_2 = 1$ fixed.  As before, both loss-limited and damped
models are equally capable of fitting the observed data.

% As above but with eta2=1 fixed!
\begin{table}
    \scriptsize
    \centering
    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$
    \label{tab:fits-all-eta2one}}
    \input{tab-fits-all-eta2one.tex}
    \tablecomments{Best damped fits select best $a_b$ value below $0.01$ from
    the range shown in Table~\ref{tab:fits-damp}, enforcing moderate damping.
    Fits for Regions 1--3, 5, 11, 12, 18, and 19 have 3 degrees of freedom; all
    others have 4.  The manual selection of a best $a_b$ value may be construed
    as removing one additional dof.}
\end{table}

% TODO EXPLAIN/DISCUSS

% As above but with eta2=1 fixed!
\begin{table}
    \scriptsize
    \centering
    \caption{Best model fits with $\Bmin = 0$ and $\mu = \eta_2 = 1$
    \label{tab:fits-all-bminzero}}

    \begin{tabular}{@{} l rr rrr @{}}
    \toprule
    {} & \multicolumn{2}{c}{Loss-limited}
       & \multicolumn{3}{c}{Damped, $a_b \leq 0.01$} \\
    \cmidrule(lr){2-3} \cmidrule(l){4-6}
    Region & $B_0$ ($\mu$G) & $\chi^2$
           & $B_0$ ($\mu$G) & $\chi^2$ & $a_b$ \\
    \midrule
    1 & 183 & 35.63 & 2.43 & 629.61 & 0.010 \\
    2 & 313 & 80.81 & 239 & 100.66 & 0.010 \\
    3 & 427 & 21.48 & 405 & 21.70 & 0.010 \\
    \cmidrule{1-6}
    4 & 285 & 51.30 & 174 & 43.82 & 0.010 \\
    5 & 289 & 19.30 & 196 & 37.33 & 0.010 \\
    6 & 411 & 174.32 & 90.2 & 61.50 & 0.005 \\
    7 & 419 & 51.30 & 277 & 11.13 & 0.006 \\
    8 & 388 & 48.06 & 205 & 9.92 & 0.006 \\
    9 & 415 & 65.45 & 143 & 14.01 & 0.005 \\
    10 & 466 & 17.28 & 307 & 1.60 & 0.005 \\
    \cmidrule{1-6}
    11 & 356 & 11.95 & 313 & 16.08 & 0.010 \\
    12 & 318 & 9.60 & 258 & 15.45 & 0.010 \\
    13 & 400 & 53.11 & 240 & 10.00 & 0.006 \\
    \cmidrule{1-6}
    14 & 384 & 103.43 & 52.3 & 9.90 & 0.005 \\
    15 & 432 & 70.66 & 255 & 20.18 & 0.005 \\
    16 & 493 & 15.13 & 430 & 3.88 & 0.006 \\
    17 & 468 & 61.84 & 194 & 29.05 & 0.004 \\
    \cmidrule{1-6}
    18 & 283 & 27.87 & 206 & 71.82 & 0.010 \\
    19 & 401 & 37.07 & 144 & 8.14 & 0.005 \\
    20 & 464 & 122.00 & 140 & 94.37 & 0.004 \\
    \bottomrule
    \end{tabular}

    \tablecomments{See comments for Table~\ref{tab:fits-all-eta2one}.}
\end{table}

@@

% First address the broad trend of leveling energy dependence in mE)
We suggest that the observed decrease in $|\mE|$ with increasing energy
(Table~\ref{tab:fwhms}) is caused by diffusion, which weakens width-energy
dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy,
$\abt0.3 \unit{keV}$ for Tycho \citep{hwang2002}.
% TODO citation if you can find it...
Diffusion should begin overtaking advection and push $\mE$ towards $0$ in soft
X-rays, as opposed to $\mE \abt -0.5$ expected for strong advection
(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
consistent with the framework of diffusive shock acceleration.

@@

% Then, degeneracy modification in the damping model
The degeneracy in $B_0$ and $\eta_2$ is modified by the presence of damping.
For small values of $a_b$ (strong damping), increased diffusion $\eta_2$ can
cause rim widths to narrow counterintuitively.  Speculatively, spatial
variation of the diffusion coefficient, which gives rise to a term $(\ptl D(x)
/ \ptl x) (\ptl f/\ptl x)$ in equation~\eqref{eq:model}, may oppose downstream
advection by imposing an effective velocity:
\begin{equation}
    v_d - \frac{\ptl D(x)}{\ptl x}
\end{equation}
thus requiring thinner rims as $\eta_2$ and $\ptl D(x) / \ptl x$ increase.

@@

% TODO Where does this go, where should we integrate this discussion about
% profile shape w.r.t. width-energy dep. fitting?

% TODO WRITE THIS CAPTION

\begin{figure*}%[ht]
    \plotone{figures/pargrid-eta2_1-model.pdf}
    \caption{A grid of best fit parameters, yay!  WRITE THIS CAPTION.}
    \label{fig:pargrid}
\end{figure*}

% --------
% srcutlog
% --------
\subsection{Synchrotron cut-off constrains diffusion}

@@

% Procedure: cont
The radio and X-ray profile modeling here contrasts strongly with our previous
width-energy fitting from X-ray measurements alone, which neglected profile
shape in favor of more robust FWHM measurements.  Manually fitting profiles
allows us to consider radio and X-ray filaments that do not have well-defined
FWHMs, especially as radio rims do not fall below 50\% of the peak emission.
We can also use profiles from regions not previously considered due to the lack
of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.
